Constraints on higher-curvature gravity theories from binary black hole ringdown signals

### 2021-11-23 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: generic title added
hs: added description of sections and todos

\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath]{revtex4-1}
\usepackage{epsfig}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{bm}
\usepackage[dvipsnames]{xcolor}
\usepackage{bm}
\usepackage{times}
% \usepackage[varg]{txfonts}
\usepackage{txfonts}
\usepackage{xspace}
\usepackage[normalem]{ulem} % To get strikethrough (\sout)
\usepackage[colorlinks]{hyperref}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{url}
\usepackage{float}
\usepackage[bottom]{footmisc}
\usepackage{lineno}
%\linenumbers
\usepackage{makecell}
\usepackage{microtype}

@@

\title{Super-awesome paper with super-cool results}

@@

@@

@@

A broad class modified gravity theories are capture by the action
%
\begin{align}
S &= \frac{1}{16 \pi G} \int \dd^4x \sqrt{-g}
\left[ R + \dots \right.
\nonumber \\
&\quad
\left.
\right]
\end{align}
%

\begin{table}[t]
\begin{tabular}{c c c c c}
\hline
\hline
Theory & $p$ & $\delta \omega$ & $\delta \tau$ & Refs. \\
\hline
\dots & \dots & \dots & \dots & \dots \\
\hline
\hline
\end{tabular}
\caption{Summary of theories consider in this paper.
\hs{Add a column with the constraint (if any) that we placed.}}
\label{tab:ref_stars}
\end{table}

@@

@@

@@

%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
\label{sec:acknowledgements}
%
We thank Emanuele Berti and Andrea Maselli for discussions.
%
The authors are grateful for the computational resources provided by the AEI,
specifically the {\sc Hypatia} cluster.
%
The authors would like to thank everyone at the frontline of the Covid-19
pandemic.
%%%%%%%%%%%%%%%%%

>>>>

\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath,longbibliography]{revtex4-2}
\usepackage{epsfig}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{bm}
\usepackage[dvipsnames]{xcolor}
\usepackage{bm}
% \usepackage{times}
% \usepackage[varg]{txfonts}
\usepackage{txfonts}
\usepackage{xspace}
\usepackage[normalem]{ulem} % To get strikethrough (\sout)
\usepackage[colorlinks]{hyperref}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{url}
\usepackage{float}
\usepackage[bottom]{footmisc}
\usepackage{lineno}
%\linenumbers
\usepackage{makecell}
\usepackage{microtype}

@@

% HS: temporary title. Feel free to add suggestions
\title{Constraints on higher-curvature gravity theories from binary black hole ringdown signals}
% \title{Black-hole ringdown as probe of higher-curvature gravity theories}

@@

\hs{Here we briefly review~\cite{Maselli:2019mjd,Carullo:2021dui}.}

@@

\hs{Here we present a short review of~\cite{Brito:2018rfr,Ghosh:2021mrv} and
explain how we modified it to include the {\sc Parspec} parametrisation.}

@@

\hs{Here we review class of gravity theories we will consider.
They all have higher-curvature terms, hence the `higher-curvature gravity theories'
in the title.}

A broad class modified gravity theories are capture by the action
%
\begin{align}
S &= \frac{1}{16 \pi G} \int \dd^4x \sqrt{-g}
\left[ R + \dots \right.
\nonumber \\
&\quad
\left.
\right]
\end{align}

@@

%%%%%%%%%%%%%%%%%
\section{Methods}
\label{sec:methods}
%%%%%%%%%%%%%%%%%

\begin{table}[th]
\begin{tabular}{c c c c c}
\hline
\hline
Theory & $p$ & $\delta \omega$ & $\delta \tau$ & Refs. \\
\hline
\dots & \dots & \dots & \dots & \dots \\
\hline
\hline
\end{tabular}
\caption{Summary of theories consider in this paper.
\hs{Add a column with the constraint (if any) that we placed.}
\hs{TODO: add which runs are done and which need to be done.}
}
\label{tab:ref_theories}
\end{table}

\hs{We {\it must very explicitly} state our working hypothesis here:
%
\begin{itemize}
    \item That we include only the nonrotating, non-GR correction to the QNMs.
    \item That due to absence of isospectrality, when translating to the theory specific result,
    we {\it chose} to use the lowest damping, gravitational QNM of the theory.
\end{itemize}
%
We can come back to these in the Sec.~\ref{sec:discussion} as things that we
might want to revisit in the future.
}

\hs{In Table~\ref{tab:ref_theories} we summarize the relevant parameters for
the {\sc Parspec} implementation of each theory and give credit to the papers
which calculated the QNMs.}

\hs{Say which GW event we will consider and justify why.}

@@

\hs{Here we summarise the results of our PE runs. Combine the posteriors on the
the non-GR parameter coming from different events. We could have a short
subsection for each theory. We should quote two thresholds for claiming
that we placed a bound, one using the secondary BH mass and another with
the final BH mass.}

@@

\hs{I think an important message of the paper is that we give indication that
there are theories of gravity (such as dCS) which can by-pass observational
constraints from the inspiral phase alone, {\it yet} they do not, if we
analyse the ringdown. This is quite important because I've frequently heard
that the ``inspiral is what will constrain theories''. I think this might be
the most important message.}

%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
\label{sec:acknowledgements}
%
We thank Emanuele Berti and Andrea Maselli for discussions.
%
\hs{Anyone else? Serguei, Deyan?}
%
We thank the computational resources provided by the AEI, specifically the
{\sc Hypatia} cluster.
%
The authors would like to thank everyone at the frontline of the Covid-19
pandemic.
%%%%%%%%%%%%%%%%%
